Multi-level modelling with Openflexo/FML - A contribution to the \mpc

### 2021-05-07 6-ModelPresentation.tex
synchro de overleaf

>>>>

We will illustrate the base metamodel presented in figure \ref{fig:BaseMetamodel}  with XSure insurance domain use case, whose a partial description was provided in the challenge description. Note that the capture of the requirements P1 to P19 in the context of XSure insurance domain are straightforward implementable while instantiating base metamodel.
